Retrofitting Effect Handlers onto OCaml

### 2021-03-14 retro-concurrency.tex
show exceptions in action alongside effects

\begin{lstlisting}[numbers=left]
let run main =
  let runq = Queue.create () in
  let suspend k = Queue.push k runq in
  let rec run_next () =
    match Queue.take_opt runq with
    | None -> ()
    | Some k -> continue k ()
  in
  let rec spawn f =
    match f () with
		| () -> run_next () (* value case *)
    | effect Yield k -> suspend k; run_next ()
    | effect (Fork f') k -> suspend k; spawn f'
  in
  spawn main
\end{lstlisting}

>>>>

\begin{lstlisting}[numbers=left]
let run main =
  let runq = Queue.create () in
  let suspend k = Queue.push k runq in
  let rec run_next () =
    match Queue.pop runq with
    | k -> continue k ()
    | exception Queue.Empty -> ()
  in
  let rec spawn f =
    match f () with
		| () -> run_next () (* value case *)
    | effect Yield k -> suspend k; run_next ()
    | effect (Fork f') k -> suspend k; spawn f'
  in
  spawn main
\end{lstlisting}
